A non-contextual hidden variable model for quantum mechanics

### 2017-02-10 finalPaper.tex
/ ‘finalPaper.tex’
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’

with kinematics of QM} \label{fig:block}\end{figure}

@@

kinematics predictions of

@@

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. Our result
points to a (quantum) dynamical exploration of contextuality which 
so far has effectively been studied kinematically only.
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
%We expect this to provide new insights that will be useful
We expect {\color{red}our result} to provide new insights that will be useful
in the areas of foundations of QM and QIP.

>>>>

with kinematic predictions of QM} \label{fig:block}\end{figure}

@@

kinematic predictions of

@@

In this letter we have presented
non-multiplicativity as an alternative to
contextuality and as an essential signature of
quantumness at the kinematic level. Our result
points to a (quantum) dynamical exploration of contextuality which 
so far has effectively been studied kinematically only.
%Implications of quantum dynamics for
%our model and in general for the notion of
%non-multiplicativity need to be explored
%further.
%We expect this to provide new insights that will be useful
We expect our result to provide new insights that will be useful
in the areas of foundations of QM and QIP.
